\section{Acknowledgements}

We would like to thank the LHC experimental Collaborations and the WLCG for their essential support. We are especially grateful for the efforts by the computing, generator and validation groups who were instrumental for the creation of large simulation samples. We thank the detector upgrade groups as well as the physics and performance groups for their input. 
We acknowledge support from CERN and from the national agencies:
CAPES, CNPq, FAPERJ and FINEP (Brazil); 
MOST and NSFC (China); 
CNRS/IN2P3 (France); 
BMBF, DFG and MPG (Germany); 
INFN (Italy); 
NWO (Netherlands); 
MNiSW and NCN (Poland); 
MEN/IFA (Romania); 
MSHE (Russia); 
MinECo (Spain); 
SNSF and SER (Switzerland); 
NASU (Ukraine); 
STFC (United Kingdom); 
NSF (USA).
We acknowledge the computing resources that are provided by CERN, IN2P3
(France), KIT and DESY (Germany), INFN (Italy), SURF (Netherlands),
PIC (Spain), GridPP (United Kingdom), RRCKI and Yandex
LLC (Russia), CSCS (Switzerland), IFIN-HH (Romania), CBPF (Brazil),
PL-GRID (Poland) and OSC (USA).
We are indebted to the communities behind the multiple open-source
software packages on which we depend.
Individual authors have received support from
AvH Foundation (Germany);
EPLANET, Marie Sk\l{}odowska-Curie Actions and ERC (European Union);
ANR, Labex P2IO and OCEVU, and R\'{e}gion Auvergne-Rh\^{o}ne-Alpes (France);
Key Research Program of Frontier Sciences of CAS, CAS PIFI, and the Thousand Talents Program (China);
RFBR, RSF and Yandex LLC (Russia);
GVA, XuntaGal and GENCAT (Spain);
the Royal Society
and the Leverhulme Trust (United Kingdom);
Laboratory Directed Research and Development program of LANL (USA).
Not least, we thank the many colleagues who have provided useful comments on the analyses. We thank I.~Bigi, S.~Hudan, A.~Khodjamirian, E.~Kou, L.~Maiani, J.~Portol\'es and K.~Trabelsi for useful comments. J. Mart\'in Camalich acknowledges support from the Spanish MINECO through the ``Ram\'on y Cajal'' program RYC-2016-20672. 
J.~Zupan acknowledges support in part by the DOE grant de-sc0011784.
W.~Altmannshofer acknowledges the National Science Foundation under Grant No. NSF-1912719. 
F.~Bishara acknowledges the Marie Sk\l{}odowska-Curie Individual Fellowship of the European Commission's Horizon 2020 Programme under contract number 745954 Tau-SYNERGIES.
A.~Carmona acknowledges the Cluster of Excellence Precision Physics, Fundamental Interactions and Structure of Matter (PRISMA-EXC1098) and grant 05H18UMCA1 of the German Federal Ministry for Education and Research (BMBF).
M.~Chala acknowledges the Royal Society under the Newton International Fellowship programme.
A.~Crivellin acknowledges the Ambizione grant of the Swiss National Science Foundation (PZ00P2 154834).
W.~Dekens acknowledges the US Department of Energy Grant No. DE-SC0009919.
S. Descotes-Genon acknowledges the EU Horizon 2020 program from the grants No. 690575, No. 674896 and No. 692194. 
A.~Esposito acknowledges the Swiss National Science Foundation under contract 200020-169696 and through the National Center of Competence in Research SwissMAP
R.~Fleischer acknowledges the Dutch National Organisation for Scientific Research (NWO).
E.~ G\'amiz acknowledges the Spanish State Research Agency (FPA2016-78220-C3-3-P) and Junta de Andaluc\'{\i}a (FQM 101).
L.-S.~Geng acknowledges the National Science Foundation of China, Grant Nos. 11522539 and 11735003.
B.~Grinstein acknowledges the US Depatment of Energy, Grant DE-SC0009919.
F.-K. Guo acknowledges the National Natural Science Foundation of China (NSFC) (Grant Nos. 11621131001, 11747601, and 11835015), the CAS Key Research Program of Frontier Sciences (Grant No. QYZDB-SSWSYS013),
the CAS Key Research Program (Grant No. XDPB09), the CAS Center for Excellence in Particle Physics.
S.~J\"ager acknowledges the UK STFC Consolidated Grant ST/P000819/1.
R.~Lebed acknowledges the U.S. National Science Foundation, Grant No. PHY-1803912.
A.~Lenz acknowledges the STFC through the IPPP grant.
J.~Matias acknowledges the FPA2014-55613-P and FPA2017-86989-P and 2017 SGR 1069. 
O. Matsedonskyi acknowledges the IASH postdoctoral fellowship for foreign researchers.
Y.~Nir acknowledges the ISF, BSF, I-CORE, Minerva.
A.~A.~Petrov acknowledges the U.S. Department of Energy, DE-SC0007983.
T.~Pich acknowledges the Spanish State Research Agency (FPA2017-84445-P) and Generalitat Valenciana [Prometeo/2017/053].
S.~Prelovsek acknowledges the Slovenian Research Agency (No.~J1-8137 and No.~P1-0035) and DFG Grant SFB/TRR 55.
S.~Schacht acknowledges the DFG Forschungsstipendium under contract no.~SCHA~2125/1-1.
D.~Shih acknowledges the US Department of Energy Grant SC0010008.
L.~Silvestrini acknowledges the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement n$^o$ 772369).
D.~van Dyk acknowledges the Deutsche Forschungsgemeinschaft (DFG) within the Emmy Noether programme under grant DY 130/1-1 and through the DFG Collaborative Research Center 110 ``Symmetries and the Emergence of Structure in QCD''.
J.~Virto acknowledges the European Union's Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 700525, `NIOBE'.
W.~Wang acknowledges the National Science Foundation of China, Grant Nos. 11575110, 11655002, 11735010.





