%
\documentclass[../report.tex]{subfiles}
\providecommand{\main}{..}
\IfEq{\jobname}{\currfilebase}{\AtEndDocument{\biblio}}{}
%
\def\Qbar    {{\kern 0.2em\overline{\kern -0.2em \PQ}{}}\xspace}

%
\newcommand{\fk}[1]{{\color{blue}#1}}
%
\newcommand{\sasa}[1]{{\color{brown}#1}}
\newcommand{\others}[1]{{\color{red}#1}}
\newcommand{\juan}[1]{{\color{green}#1}}
\definecolor{gold}{rgb}{1.0, 0.65, 0.0}
\newcommand{\ale}[1]{{\color{gold}#1}} 
%
%


\begin{document}

\section{Hadron spectroscopy and QCD exotica}
{\it \small Authors (TH): Angelo Esposito, Feng-Kun Guo, Juan Nieves, Alessandro Pilloni, Antonio Polosa, Sasa Prelovsek.}

%
\Blu{Determination of hadron spectrum is key to understanding the strong interactions, in particular the mechanisms underlying color confinement.}
While \Blu{BESIII is the leading experiment in the charm region, and} \belletwo will make a major impact 
in the study of excited mesons and lighter exotic hadrons, only the HL-LHC experiments 
have the potential to comprehensively study the full range of possible excited
hadronic states. Such a comprehensive understanding and characterisation of quark
structures would not only, in some sense, greatly enhance the taxonomy of the SM particles, but
would also sharpen our understanding of QCD in a particularly difficult energy
regime. Moreover, while not directly probing BSM physics, spectroscopy
measurements will continue to make essential contributions to the interpretation
of any observed BSM effects in the flavour sector. In addition, spectroscopy can provide tools to probe BSM effects by using a new observed state as a tagger\cite{LHCb-PAPER-2017-023}, \cite{LHCb-PAPER-2016-039}.

While the \upgradetwo of LHCb will
by design offer unparalleled capabilities in this area, the legacy of HL-LHC for
spectroscopy will be much stronger, if ATLAS and CMS are also able to continue to
pursue this work in the HL-LHC period. The planned hardware tracking
triggers and much higher data rates sent to their software triggers are promising
in this respect, and we encourage further study of what capabilities they might bring to this area of physics. 
\Blu{In particular, heavy-ion experiments might have an advantage for doubly-heavy exotics, if they can improve their particle identification.}

\Blu{Gauge theories play a major role in BSM and some of them might be strongly coupled. 
In this sense, QCD serves as a prototype of a strongly-coupled gauge theory. By studying hadron spectroscopy and the QCD exotica we learn about the range of possibilities of analogous states in BSM theories.}

\input{section6/theory}
\input{section6/experimental}

%
%

\end{document}
