% don't remove the folling lines, and edit the defintion of \main if needed
\documentclass[../report.tex]{subfiles}
\providecommand{\main}{..}
\IfEq{\jobname}{\currfilebase}{\AtEndDocument{\biblio}}{}
% until here
\def\bsmumu{\ensuremath{B^0_s \to \mu^{+} \mu^{-}}\xspace}
\def\bsmumugamma{\ensuremath{B^0_s \to \mu^{+} \mu^{-} \gamma}\xspace}
\def\bdmumugamma{\ensuremath{B^0 \to \mu^{+} \mu^{-} \gamma}\xspace}
\def\epm    {{\ensuremath{e^\pm}}\xspace}
\def\emp    {{\ensuremath{e^\mp}}\xspace}
\def\mupm   {{\ensuremath{\mu^\pm}}\xspace}
\def\mump   {{\ensuremath{\mu^\mp}}\xspace}
\def\BToEMu    {\decay{\B}{\epm\mump}}
\def\BdToEMu   {\decay{\Bd}{\epm\mump}}
\def\BsToEMu   {\decay{\Bs}{\epm\mump}}
\newcommand{\subdecay}[2]{\ensuremath{#1(\!\to #2)}\xspace}
% Particles
\def\mupm   {{\ensuremath{\mu^\pm}}\xspace}
\def\mump   {{\ensuremath{\mu^\mp}}\xspace}
\def\taupm   {{\ensuremath{\tau^\pm}}\xspace}
\def\taump   {{\ensuremath{\tau^\mp}}\xspace}
%% Decays
\def\tauppp{\decay{\taupm}{\pi^\pm\pi^\mp\pi^\pm\nu}}
\def\tauppppi0{\decay{\taupm}{\pi^\pm\pi^\mp\pi^\pm\piz\nu}}
\def\BToTauMu    {\decay{\B}{\taupm\mump}}
\def\BdToTauMu   {\decay{\Bd}{\taupm\mump}}
\def\BsToTauMu   {\decay{\Bs}{\taupm\mump}}
\def\BdToTauMupm   {\decay{\Bd}{\taupm\mump}}
\def\BsToTauMupm   {\decay{\Bs}{\taupm\mump}}
\def\BdsToTauMu   {\decay{\B^0_{\left( s\right) }}{\taupm\mump}}
\def\BdsToTauMuSS {\decay{\B^0_{\left( s\right) }}{\taupm\mupm}}
\def\Btaumu{\decay{\B}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bstotaumu{\decay{\Bs}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bdtotaumu{\decay{\Bd}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bdstaumu{\decay{\B^0_{\left( s\right) }}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bdtaumu{\decay{\Bd}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bstaumu{\decay{\Bs}{\subdecay{\taupm}{\pipm\pimp\pipm\nu}\mump}}
\def\Bstaumupi0{\decay{\Bs}{\subdecay{\taupm}{\pipm\pimp\pipm\piz\nu}\mump}}
\def\Bdtaumupi0{\decay{\Bd}{\subdecay{\taupm}{\pipm\pimp\pipm\piz\nu}\mump}}
\def\BToDPi    {\decay{\Bd}{\D^\pm\pi^\mp}}
\def\dbtaunu {\decay{\B}{D^{(*)} \tau \nu}}
\def\dbmunu {\decay{\B}{D^{(*)} \mu \nu}}
\def\dbenu {\decay{\B}{D^{(*)} e \nu}}
\def\dmunu {\decay{\B}{D \mu \nu}}
\def\denu {\decay{\B}{D e \nu}}
\def\dsttaunu {\decay{\B}{D^{*} \tau \nu}}
\def\dstztaunu {\decay{\B}{D^{*0} \tau \nu}}
\def\dstptaunu {\decay{\B_{d}}{D^{*-} \tau^{+} \nu}}
\def\dstmunu {\decay{\B}{D^{*} \mu \nu}}
\def\dstenu {\decay{\B}{D^{*} e \nu}}
\def\dstpmunu {\decay{\B}{D^{*+} \mu \nu}}
\def\dstzmunu {\decay{\B}{D^{*0} \mu \nu}}
\def\dstlnu {\decay{\B}{D^{*} \ell \nu}}
\def\dblnu {\decay{\B}{D^{(*)} \ell \nu}}
\def\RDst {\ensuremath{\mathcal{R}(\Dstar)}\xspace}
\def\RDstp {\ensuremath{\mathcal{R}(\Dstarp)}\xspace}
\def\RD {\ensuremath{\mathcal{R}(D)}\xspace}
\def\RDb {\ensuremath{\mathcal{R}(D^{(*)})}\xspace}
\def\RDst {\ensuremath{\mathcal{R}(\Dstar)}\xspace}
\def\RDorDst {\ensuremath{\mathcal{R}(D^{(*)})}\xspace}
\def\RDsteq {\ensuremath{\mathcal{R}(\Dstar)\equiv\frac{\mathcal{B}\left(\decay{\B}{\Dstarb\taup\neu}\right)}{\mathcal{B}\left(\decay{\B}{\Dstarb\ellp\neu}\right)}}\xspace}
\def\Req {\ensuremath{\mathcal{R}(D^{*})\equiv\frac{\mathcal{B}\left(\decay{\B}{\Db^{(*)}\taup\neu}\right)}
         {\mathcal{B}\left(\decay{\B}{\Db^{(*)}\ellp\neu}\right)}}\xspace}
\def\RD {\mathcal{R}(D)}
\def\threepim {\ensuremath{\pim \pip \pim}\xspace}
\def\threepip {\ensuremath{\pip \pim \pip}\xspace}
\def\mupm   {{\ensuremath{\mu^\pm}}\xspace}
\def\mump   {{\ensuremath{\mu^\mp}}\xspace}
\def\taupm   {{\ensuremath{\tau^\pm}}\xspace}
\def\taump   {{\ensuremath{\tau^\mp}}\xspace}
%% Decays
\def\taummm{\decay{\taupm}{\mupm \mu^+ \mu^-}}
\def\Dsetamunu{\decay{\Ds}{\subdecay{\eta}{\mu^+\mu^-\gamma}\mu^+\nu_{\mu}}}

\begin{document}

\section{Bottom-quark probes of new physics and prospects for $B$-anomalies \label{secBanom}}
\label{sec:7}


A key contribution of the HL-LHC data sets will be a comprehensive global picture of rare and (semi)-leptonic quark transitions. This has value whether or not the current ``flavour anomalies'' are confirmed with Run~2 or Run~3 LHC data. If the improvements on statistically limited observables, $R_{K^{(*)}}$ and $R(D^{(*)})$,  
%which 
%are most statistically sensitive ($R_{K}$ and \RDb) 
confirm the anomalies, a  global analysis of all related channels may 
%provide a way to 
discriminate between different 
%the full range of possible 
BSM explanations. Such a global analysis will also help to constrain the mass scale of the BSM particles and mediators, which, together with the direct HL-LHC searches, will further restrict the range of possible explanations for the anomalies. On the other hand, if the signifcance of the anomalies decreases, or they even disappear with Run 2 and Run 3 data, we should still search 
%may return to searching 
for small BSM
effects on top of the dominant SM amplitudes. In this case, global analyses of the data would lead to improved bounds on the BSM affecting these flavor observables. The statistical power of the HL-LHC datasets will also enable a unique reach for other BSM signatures such as Lepton-Flavour Violation (LFV) and Baryon-Number Violation (BNV), particularly in the baryon and heavy-meson sectors.

We would like to stress that, in the HL-LHC era, many rare beauty decays will become abundant and enter the precision-measurement regime. Therefore, it will  become increasingly important that the LHC collaborations and Belle II publish results in such a way that systematic uncertainties can be treated in a coherent manner and their correlations taken into account. 
A good example of this is the treatment of the ratio of
hadronization fractions $f_s/f_d$ in any LHC $B_q\to \ell\ell$ combination, discussed 
%further 
in Sec.~\ref{sec:7_exp}. It will also be important to correctly treat systematic uncertainties due to the use of common software packages, e.g., the use of {\tt PHOTOS} by  the LHC experiments and Belle~II, in future lepton universality measurements.

While much of the power of the HL-LHC and Belle~II datasets will lie in the breadth of precisely measured rare and (semi-)leptonic decays, practical considerations mean that experiments will continue to publish analyses of individual decay modes as each is completed. Systematically publishing experimental likelihoods, efficiency maps, and resolution unfoldings, as already done for some of the most important analyses, should be strongly encouraged even now. 
%at this stage, since
% .
% It will therefore be particularly important to provide these results in a way which 
This facilitates both the combination of results between experimental collaborations, and the inclusion of the results in global fits and in tests of phenomenological models~\cite{Hurth:2017sqw,Blake:2017fyh,Chrzaszcz:2018yza}. 


\subsection{Phenomenology of $b\to s \ell\ell$ decays}
{\it\small Authors (TH): Wolfgang Altmannshofer,  David Straub, Javier Virto.}

\input{section7/bsll.tex}

\subsection{Phenomenology of $b\to c \ell \nu$ decays}
{\it\small Authors (TH): Marat Freytsis, Martin Jung, Dean Robinson, Stefan Schacht.}

\label{sec:7_RDs}
\input{section7/bctaunu.tex}


\input{section7/experimental}

%\subsection{Combined theory/experiment perspective on global interpretations (EFT/non-EFT)}
%a particular emphasis on impact of LHC-only combined analysis and complementarity of this with Belle II

%Needs to be expanded, Belle II brought into it...
%Bring in the topic of non-EFT explanations? Keep looking for new light degrees of freedom?
\end{document}
